---
title: "Q1_6"
author: "Kamin Atsavasirilert"
date: "2023-10-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1.6 Week7

# When we use the initial values obtained from the moment matching method, the optimal values converge faster than using the initial values given by the question 1.2.

Optimizing with given initial values in question 1.2 (took 22 time units to converge)
```{r cars}
data = read.csv("C:/min/coding_project/IE522_Statistical_Methods_in_Finance/Week7/ZM.csv")
log_ret = diff(log(data$ZM))

t = 1/252
initial_val_NIG = c(10,0,2,0)
NIG = function(x, theta){
  tmp_val = sqrt((theta[3] * t)^2 + (x - theta[4] * t)^2)
  (theta[1] * theta[3] * t / pi)* besselK(theta[1] * tmp_val, 1) / tmp_val * exp(theta[3] * sqrt(theta[1]^2 - theta[2]^2) * t + theta[2] * (x - theta[4] * t))
}

resultNIg = optim(initial_val_NIG, fn=function(theta){-sum(log(NIG(log_ret, theta)))}, method = "L-BFGS-B")
resultNIg
```

Optimizing with initial values obtained by moment matching method (took 17 time units to converge)
```{r cars2}
initial_val_NIG = c(15.39977,4.091474,7.501373,-0.7332863)

resultNIg_with_moment_matching = optim(initial_val_NIG, fn=function(theta){-sum(log(NIG(log_ret, theta)))}, method = "L-BFGS-B")
resultNIg_with_moment_matching
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
