---
title: "Q1_8"
author: "Kamin Atsavasirilert"
date: "2023-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1.8 Week7
# The estimates obtained from both methods are very close to each other.
- mu_hat: theoretical value = 0.002542841, numerically-solved value = 0.002640584
- b_hat: theoretical value = 0.03175852, numerically-solved value = 0.031760275

# The value of log likelihood function exactly matches what I get from the previous question until 4 digit decimal points.
From https://en.wikipedia.org/wiki/Laplace_distribution, the MLEs of mu and b of a laplace distribution are as follows.

$$\hat{\mu_x} = median(x_i)$$
and
$$\hat{b_x} = (\Sigma_{i = 1}^{n} |x_i - \hat{\mu}_x|)/n$$

```{r cars}
data = read.csv("C:/min/coding_project/IE522_Statistical_Methods_in_Finance/Week7/ZM.csv")
log_ret = diff(log(data$ZM))

mu_hat = median(log_ret)
b_hat = mean(abs(log_ret - mu_hat))
cat("mu_hat:",mu_hat)
cat("b_hat",b_hat)
laplace_dist = function(x, theta){
  (exp(-abs(x-theta[1])/theta[2]))/(2*theta[2])
}

log_likelihood_function = function(theta){
  sum(log(laplace_dist(log_ret, theta)))
}
cat("the value of the log likelihood function using theoretical MLEs:",log_likelihood_function(c(mu_hat, b_hat)))

```