---
title: "Q2_2"
author: "Kamin Atsavasirilert"
date: "2023-10-03"
output: html_document
---

```{r setup, include=FALSE}
```

## Q2.2 Week6
# For  Shapiro-Wilk test, the P-value is much less than 0.05, meaning that we accept the alternative hypothesis that the TSLA stock returns did not come from a normal distribution.


```{r cars}
library(moments)

data = read.csv("C:/min/coding_project/IE522_Statistical_Methods_in_Finance/Week6/TSLANVDA.csv")
log_ret_tsla = diff(log(data$TSLAAdjClose), lag=1)

shapiro.test(log_ret_tsla)
```

# For  Jarque-Bera test, the P-value is much less than 0.05, meaning that we accept the alternative hypothesis that the TSLA stock returns did not come from a normal distribution.

```{r cars2}
jarque.test(log_ret_tsla)
```

# The sample kurtosis also greater than 3, and we can also clearly see that the TSLA return data did not follow a normal distribution from the normal Q-Q plot.
```{r cars3}
cat("kurtosis:", kurtosis(log_ret_tsla))
qqnorm(log_ret_tsla, xlab = "Theoretical Normal quantile", ylab = "Sample quantile")
qqline(log_ret_tsla)
```